---
title: "Miscellaneous exports and petitions"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
    pdf_document:
       number_sections: true
       toc: true
       toc_depth: 4
---


```{r setup}
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 70), tidy = TRUE, connection="fracking_db", max.print=50)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  paste0("\n \\", "footnotesize","\n\n", x, "\n\n \\normalsize\n\n")
})
require(openxlsx)
require(RPostgreSQL)

```

```{r}
fracking_db <- dbConnect(PostgreSQL(), dbname='fracking')
```


# Recapitulative ANH, event_id coordinates and habitat

See Francisco's mail (27/02/2023 09:49).

## Coordinates of each event

For events with line geometries, the second point of the line is extracted!
All coordinates in SRID 3116 (<https://spatialreference.org/ref/epsg/magna-sirgas-colombia-bogota-zone/>).

```{sql, output.var="coord_events"}
WITH e_lines AS(
SELECT event_id, name_pt_ref, biol_gp, aquatic,(ST_dumpPoints(li_geom)).*
FROM main.event e
LEFT JOIN main.gp_event ge USING (cd_gp_event)
LEFT JOIN main.def_gp_biol dgp USING (cd_gp_biol)
LEFT JOIN main.punto_referencia USING (cd_pt_ref)
WHERE li_geom IS NOT NULL
)
SELECT a.* 
FROM 
((
SELECT event_id, name_pt_ref, biol_gp, aquatic,
    ST_X(e.pt_geom) x_coord_3116, ST_Y(pt_geom) y_coord_3116
FROM main.event e
LEFT JOIN main.gp_event ge USING (cd_gp_event)
LEFT JOIN main.def_gp_biol dgp USING (cd_gp_biol)
LEFT JOIN main.punto_referencia USING (cd_pt_ref)
WHERE pt_geom IS NOT NULL
)
UNION
(
SELECT event_id, name_pt_ref, biol_gp, aquatic,
    ST_X(geom), ST_Y(geom)
FROM e_lines
WHERE path=ARRAY[2]
)) a
LEFT JOIN main.punto_referencia pr USING (name_pt_ref)
ORDER BY num_anh,biol_gp
```

## Recap by anh number

```{sql output.var="anh_recap"}
SELECT name_pt_ref, ARRAY_AGG(DISTINCT biol_gp) biol_gps, ARRAY_AGG(DISTINCT event_id) event_ids
FROM main.event e
LEFT JOIN main.gp_event ge USING (cd_gp_event)
LEFT JOIN main.def_gp_biol dgp USING (cd_gp_biol)
LEFT JOIN main.punto_referencia USING (cd_pt_ref)
GROUP BY name_pt_ref, num_anh
ORDER BY num_anh
```

## Habitats/landcover

* landcov_from_event_coord is the landcover from the intersection between landcover map and coordinates
* landcov_db_event is the landcover from the database at the event level
* landcov_db_gp_event is the landcover from the database at the gp_event (ANH + gp_biol + Method) level


```{sql output.var="habitat_landcover"}
WITH e_lines AS(
SELECT event_id, name_pt_ref, biol_gp, aquatic, cd_gp_event, cd_event, (ST_dumpPoints(li_geom)).*
FROM main.event e
LEFT JOIN main.gp_event ge USING (cd_gp_event)
LEFT JOIN main.def_gp_biol dgp USING (cd_gp_biol)
LEFT JOIN main.punto_referencia USING (cd_pt_ref)
WHERE li_geom IS NOT NULL AND NOT aquatic
)
SELECT a.event_id, a.biol_gp, dl.landcov landcov_from_event_coord, he.habitat landcov_db_event, lget.landcov landcov_db_gp_event
FROM 
((
SELECT event_id, name_pt_ref, biol_gp, aquatic,cd_gp_event,cd_event,
    pt_geom
FROM main.event e
LEFT JOIN main.gp_event ge USING (cd_gp_event)
LEFT JOIN main.def_gp_biol dgp USING (cd_gp_biol)
LEFT JOIN main.punto_referencia USING (cd_pt_ref)
WHERE pt_geom IS NOT NULL AND NOT aquatic
)
UNION
(
SELECT event_id, name_pt_ref, biol_gp, aquatic,cd_gp_event,cd_event,
    geom
FROM e_lines
WHERE path=ARRAY[2]
)) a
LEFT JOIN main.punto_referencia pr USING (name_pt_ref)
LEFT JOIN landcov_gp_event_terrestrial lget USING(cd_gp_event)
LEFT JOIN habitat_event he USING (cd_event)
LEFT JOIN spat.landcov l ON ST_intersects(a.pt_geom,l.the_geom)
LEFT JOIN spat.def_landcov dl ON l.cd_landcov=dl.cd_landcov
--WHERE dl.landcov<>he.habitat OR dl.landcov<>lget.landcov OR he.habitat<>lget.landcov
ORDER BY num_anh,biol_gp
```

## Exporting

```{r}
source("saveInExcel.R")
save_in_excel("recapCoordLandcovAnh.xlsx",list(habitat_landcover=habitat_landcover,anh_recap=anh_recap,coord_events=coord_events))
```

